visitation_bias

### 2021-02-13 code/preference_lability.Rmd
update

ggplot(bb_traits, aes(pbl.w, pbl.w.durieaux,
                      color = bb.sp, pch = factor(pbl.w.class2))) +
  geom_point()

@@

# If I want to make inference about species visitation rates, I don't need the tongue-length class effect; I just need the site effect. But, when I want to make inference about the tongue length classes, I do need the species-level effect.
brm_pvis02 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 | site), # a random intercept and slope for ktype:site
                  family = "bernoulli", 
                  #file = "../output/brm_pvis_ktype_02",  # for running locally
                  file = "brm_pvis_ktype_02", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))
```
## 1.3 Evaluate models
```{r}
# Summary
summary(brm_pvis00)
summary(brm_pvis01)
summary(brm_pvis02)

@@

ggsave(file = "../output/brm_pvis01_plot1.png", width = 5, height = 7)
ggsave(file = "../output/brm_pvis01_plot1.pdf", width = 5, height = 7)
```

@@

diet_breadth <- full_join(taxon_diet_breadth, morph_diet_breadth)

@@

ggplot(diet_breadth, aes(morph.diet.breadth, tax.diet.breadth, color = bb.sp)) +
  geom_point() +
  geom_smooth(method = "lm")
```

>>>>

@@

# If I want to make inference about species visitation rates, I don't need the tongue-length class effect; I just need the site effect. But, when I want to make inference about the tongue length classes, I do need the species-level effect.
brm_pvis02 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 | site), # a random intercept and slope for ktype:site
                  family = "bernoulli", 
                  #file = "../output/brm_pvis_ktype_02",  # for running locally
                  file = "brm_pvis_ktype_02", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))
```

## 1.3 Evaluate models
```{r}
# Summary
summary(brm_pvis00)
summary(brm_pvis01)
summary(brm_pvis02)

@@

ggsave(file = "../output/brm_pvis01_plot1.png", width = 5, height = 7)
ggsave(file = "../output/brm_pvis01_plot1.pdf", width = 5, height = 7)

ggplot(brm_pvis01_plotframe1, aes(condition_mean_trans, ktype, 
                                 xmin = .lower_trans, xmax = .upper_trans)) +
  geom_pointinterval() +
  theme_light(18) +
  labs(x = "Visitation probability", y= "Morphotype") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis01_plot1_largeprint.png", width = 7, height = 5)

@@

diet_breadth <- full_join(taxon_diet_breadth, morph_diet_breadth) %>%
  left_join(site_data)

@@

ggplot(diet_breadth, aes(morph.diet.breadth, tax.diet.breadth, color = bb.sp)) +
  geom_point() +
  geom_smooth(method = "lm")

ggplot(diet_breadth, aes(elev.mean, tax.diet.breadth)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~bb.sp)

ggplot(diet_breadth, aes(elev.mean, morph.diet.breadth)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~bb.sp)
```
